Preliminary Thesis Defence

### 2013-12-29 bitattack.tex
clean chapter pages

\begin{refsection}
\chapter{Bitcoin Attacks: Or How Cryptocurrencies Gain Momentum}
As discussed in \autoref{btc}, there has been a new phenonemon in international finance called cryptocurrencies. The first of these was the cryptocurrency called Bitcoin \parencite{nakamoto2008bitcoin}. However, soon after Bitcoin started gaining momentum, alternative crypotcurrencies where being designed. All of these cryptocurrencies are based to a large extend on the Bitcoin protocol, but often introduce small technological innovations.

@@

My idea is to adapt standard models of currency attacks such as in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models} to model the gaining of long (v.s.~currency attacks' short) momentum for cryptocurrencies. Initially we would model how a currency can gain sufficient momentum to establish itself as a stably above zero.

This could later be expended to a model with several cryptocurrencies competing for the investment of the same new cryptocurrency adopt, who is converting his/her fiat currency into one of several cryptocurrencies.

>>>>

\begin{refsection}
\chapter{Bitcoin Attacks: Or How Cryptocurrencies Gain Momentum}
\label{bitatt}
\vspace{\stretch{1}}
\section*{Abstract}
In this chapter I set out the idea of employing the models used for currency attacks,
to analyse how cryptocurrencies gain momentum.
Additionaly, I discuss how inflation in the cryptocurrency economy is possible.
\pagebreak

\section{Introduction}
As discussed in \autoref{btc}, there has been a new phenonemon in international finance called cryptocurrencies.
The first of these was the cryptocurrency called Bitcoin \parencite{nakamoto2008bitcoin}.
However, soon after Bitcoin started gaining momentum, alternative crypotcurrencies where being designed.
All of these cryptocurrencies are based to a large extend on the Bitcoin protocol,
but often introduce small technological innovations.

@@

\section{Positive Currency Attacks}
My idea is to adapt standard models of currency attacks such as in 
\textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}
to model the gaining of long (v.s.~currency attacks' short) momentum for cryptocurrencies.
Initially we would model how a currency can gain sufficient momentum to establish itself as a stably above zero.

\subsection{A Multi-currency Model}
This could later be expended to a model with several cryptocurrencies,
competing for the investment of the same new cryptocurrency adopt,
who is converting his/her fiat currency into one of several cryptocurrencies.

\section{Multi-cryptocurrency Economy and Inflation}
Finally, an extension of such a multi-cryptocurrency model can provide a valuable insight into the issue of inflation.

On of the key selling points of the cryptocurrencies, and equally one of the key critisism of many economics
(e.g.~Paul Krugman), is that there is no inflation in a crypocurrency.
The crypocurrencies are designed specifically so that inflation eventually becomes impossible (once all coines are mined).

However, it is key here to understand the economy as a multi-cryptocurrency object.
Since creating a currency can be done at negligable cost,
and the only value of the cryptocurrency lies in its utility as a mechanism for transactions,
more cryptocurrencies will come into existance.
Especially since it is very simple for a merchant to accept several cryptocurrencies as a form of payment.
The effect of this will be that inflation in each cryptocurrency will remain as defined,
however, the cryptocurrency economy as a whole, will be able to experience inflation.

Additionaly, this partly addresses one of social critiques of Bitcoin,
namely the issue of bitcoin mining being excessively wastful.
Bitcoin mining does not produce anything of any social value (not unlike gold mining),
the higher value of bitcoin, the more computing power (and electricity) will be diverted to this.
However, in a multi-currency model, it will be more effective to mine alternative cryptocurrencies,
as these can initially be mined with relative ease.

### 2013-12-29 bitremit.tex
clean chapter pages

\begin{refsection}
\chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
\label{btc}
In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC). 
This currency -the first of a group called cryptocurrencies- has the following economics features:

>>>>

\begin{refsection}
\chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
\label{bitremit}
\vspace{\stretch{1}}
\section*{Abstract}
In this chapter I describe the basis of cryptocurrencies, particularly Bitcoin.
I give an overview of what sources of data are available for analysis, and how these can be employed.
I propose a project which enables simple telephones or `stupid phones' to perform bitcoin transaction,
this can provide insights into the remittances that are transacted in Bitcoin.
\pagebreak

\section{Introduction}
In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC). 
This currency -the first of a group called cryptocurrencies- has the following economics features:
